Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-03-08 manuscript 01/index.qmd
table_2 complete?

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)

@@

with_dir(here(), tar_load(ich_aggressive))

@@

The analysis code is publicly available as outlined by the NINDS Data Request Agreement at [https://github.com/nikhilpatelmd/ich-laterality](https://github.com/nikhilpatelmd/ich-laterality).

@@

A total of `r sample_size` patients were included in the analysis, of which `r left_hemisphere_count` (`r left_hemisphere_count/sample_size`) had left hemispheric ICH. They had higher NIHSS scores, higher GCS scores, and lower rates of hypertension as compared to those with right hemispheric ICH (@tbl-1).

@@

theme_gtsummary_compact(set_theme = TRUE, font_size = 14)
with_dir(here(), tar_read(table_1_aggressive))

@@

::: {.callout-note}
What am I trying to do here? I want to present the results of the logistic regression showing that after controlling for other factors, there is still a higher probability of a right-hemisphere ICH patient receiving neurosurgical intervention.

I have to change the baseline factor in `ich_laterality` to "Left".

I should report the following: point estimate, 95% CIs, and posterior probability that effect is greater than 0, or for minimal clinically important difference.
:::

```{r neurosurgery}
neurosurgery_mod <- with_dir(here(), tar_read(m_posterior_neurosurgery_canonical))

table_2 <- with_dir(here(), tar_read(table_2_aggressive))

summary <- modelsummary(models,
  exponentiate = TRUE,
  fmt = fmt_significant(3),
  estimate = "{estimate}",
  statistic = "{conf.low} - {conf.high}",
  coef_omit = "^(?!b_ich_lat)",
  coef_rename = c("b_ich_lateralityRight" = "Right Hemisphere ICH"),
  gof_map = c("none")
)

@@

ult_table <- bind_rows(table1, table2)

ult_table <- t(ult_table)
```

>>>>

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

@@

# load data and models
with_dir(here(), tar_load(ich_aggressive))

@@

As outlined in the NINDS Data Request Agreement, the analysis code is publicly available at [https://github.com/nikhilpatelmd/ich-laterality](https://github.com/nikhilpatelmd/ich-laterality).

@@

A total of `r sample_size` patients were included in the analysis, of which `r left_hemisphere_count` (`r percent(left_hemisphere_count/sample_size, digits = 1)`) had left hemispheric ICH. They had higher NIHSS scores, higher GCS scores, and lower rates of hypertension as compared to those with right hemispheric ICH (@tbl-1).

@@

with_dir(here(), tar_read(table_1_aggressive)) |>
  as_flex_table() |>
  font(part = "all", fontname = "Figtree") |>
  fontsize(size = 11, part = "header") |>
  fontsize(size = 10) |>
  theme_zebra() |>
  line_spacing(space = 1.25, part = "all") |>
  padding(padding = 4, part = "all")

@@

```{r neurosurgery}
#| label: tbl-2
#| tbl-cap: "Association between hemispheric lateralization and care"#|

summary <- modelsummary(models,
  exponentiate = TRUE,
  fmt = 2,
  estimate = "{estimate}",
  statistic = "{conf.low} - {conf.high}",
  coef_omit = "^(?!b_ich_lat)",
  coef_rename = c("b_ich_lateralityRight" = "Right Hemisphere ICH"),
  gof_map = c("none")
)

@@

pre_tab <- as_tibble(t(bind_rows(table1, table2)))

table_2 <- with_dir(here(), tar_read(table_2_aggressive))
tibble_2 <- as_tibble(table_2) |> select(-1)

column_names <- c(
  "Neurosurgical Intervention",
  "External Ventricular Drain",
  "Tracheostomy",
  "Days of Mechanical Ventilation",
  "Withdrawal of Life-Sustaining Therapy",
  "Early Withdrawal of Life-Sustaining Therapy",
  "DNR Order"
)

combined <- bind_cols(column_names, tibble_2, pre_tab) |>
  rename(
    "Right Hemisphere" = "**Right**, N = 1,757",
    "Left Hemisphere" = "**Left**, N = 1,720",
    "Outcome" = ...1,
    "aOR" = V1,
    "95% Credible Interval" = V2,
    "Probability of Difference (aOR >1)" = V3,
    "% ROPE" = V4
  )

flextable(combined) |>
  font(part = "all", fontname = "Figtree") |>
  fontsize(size = 10) |>
  theme_zebra() |>
  line_spacing(space = 1.25, part = "all") |>
  padding(padding = 4, part = "all") |>
  bold(part = "header") |>
  bold(i = 1) |>
  padding(padding = 5, part = "all") |>
  width(width = 50, j = 1) |>
  width(width = 2, j = 2:3) |>
  width(width = 4, j = 4:6)
